Network Deliberation: The role of network structure in large-scale, internet-enabled, participatory decision-making

### 2021-09-28 ch-experiment.tex
Add pilots.

The initial pilot study was conducted on December 21, 2018,
before the custom online platform was developed.
In this pilot, NUMBER participants engaged in a synchronous 60-minute deliberation.
Participants sat at individual computer workstations, separated by dividers.
Participants discussed the following question:
``Where should the use of electric scooters be permitted?''
Participants were placed in a single treatment group, and divided into 4
pods of size 4--5.
These pods were reassigned using the random-pod method for a total of three
rounds.
The deliberation took place in chat rooms running the free and open-source
OTree online experiment software.

The second pilot took place after the initial development of the custom online
platform, from August 24, 2020 through August 32, 2020.

The third pilot took place from August 23, 2021 through August 29, 2021.

@@

One possibility is to measure the distance from strong unanimity.
Two such methods will be used to analyze the results of the deliberation experiment:
the mean Kendal tau metric and the mean Spearman correlation.
The Kendal tau metric is the number fraction of pairwise contests that have
different results between two profiles \cite{kendall_new_1938}}.
By averaging this measure over all pairs of members, an overall measure of agreement can be calculated for the group.
This measure does not incorporate information about win/loss margins,
only whether an alternative wins or loses.
To quantify the win/loss margin, the mean Spearman correlation will be used.
The Spearman correlation is the linear coefficient of correlation between the
rank orders of alternatives for two voters \cite{spearman_proof_1904}.
As with Kendall tau, the Spearman correlation can be averaged over all pairs of
members to determine a measure of agreement for the entire group.
It must be noted that representing agreement with a single number will inevitably
ignore important information.
Neither of these measures distinguishes a small number of voters disagreeing
on many comparisons from a large number of voters disagreeing on a few.
The Spearman correlation is also unable to distinguish these from situations in
which a small number of voters disagree by a very large margin.

>>>>

The initial pilot study was conducted on December 21, 2018,
before the custom online platform was developed.
In this pilot, 18 participants engaged in a synchronous 60-minute deliberation.
Participants sat at individual computer workstations, separated by dividers.
Participants discussed the following question:
``Where should the use of electric scooters be permitted?''
Participants were placed in a single treatment group, and divided into 4
pods of size 4--5.
These pods were reassigned using the random-pod method for a total of three
rounds.
The deliberation took place in chat rooms running the free and open-source
OTree online experiment software \cite{chen_oTree_2016}.

The second pilot took place after the initial development of the custom online
platform, from August 24, 2020 through August 32, 2020.
In this pilot, 7 participants engaged in an asynchronous deliberation over the
course of 7 days.
Participants were assigned to a single treatment group using network deliberation
with random-pod assignment.
Pods were size 4, and there were 3 rounds (2, 2, and 3 days).
Participants were researchers considering a week-long collaboration and
deliberated on the following question:
``What is your current preference for week of science topics?''

The third pilot took place from August 23, 2021 through August 29, 2021.
Participants deliberated on the following question:
``How should schools in the US reopen for fall 2021?''
Participants were recruited on reddit and Twitter.
18 participants were enrolled (excluding several identified as fake accounts).
These participants were divided between a conventional deliberation control
group and a random-pod treatment group.
The random-pod treatment group had two pods of size 5.
Deliberation was divided into 3 rounds (2, 2, and 3 days).

In these pilots, participants showed quantitative and qualitative evidence of
changing their preferences over the course of deliberation.
Here is an example of one such interaction:
\begin{quote}
{\bfseries Aspen Sunflower:} Even though my \#1 choice includes mandatory vaccinations, I know it's not possible due to school starting now AND MDHS can't mandate it yet. Based on previous stage, I think most seemed to want vaccinations but also wanted options. One option doesn't fit all students.

{\bfseries Aspen Poppy:} Major gap in my understanding here! The schools do not mandate vaccines for students, the state does. For the 12-17 age group, the vaccine is authorized under emergency use, full FDA approval is pending. This strengthens my desire to see hybrid learning with smaller in person groups and vaccinated staff.
\end{quote}

While the pilots did not have enough participants to identify any differences
in the evolution of preferences between different treatment groups,
evidence that preferences do change through deliberation affirms the central
assumption of this dissertation and further motivates the question of how
communication network structure influences that evolution.

@@

One possibility is to measure the distance from strong unanimity.
Two such methods will be used to analyze the results of the deliberation experiment:
the mean Kendal tau metric and the mean Spearman correlation.
The Kendal tau metric is the number fraction of pairwise contests that have
different results between two profiles \cite{kendall_new_1938}.
By averaging this measure over all pairs of members, an overall measure of agreement can be calculated for the group.
This measure does not incorporate information about win/loss margins,
only whether an alternative wins or loses.
To quantify the win/loss margin, the mean Spearman correlation will be used.
The Spearman correlation is the linear coefficient of correlation between the
rank orders of alternatives for two voters \cite{spearman_proof_1904}.
As with Kendall tau, the Spearman correlation can be averaged over all pairs of
members to determine a measure of agreement for the entire group.
It must be noted that representing agreement with a single number will inevitably
ignore important information.
Neither of these measures distinguishes a small number of voters disagreeing
on many comparisons from a large number of voters disagreeing on a few.
The Spearman correlation is also unable to distinguish these from situations in
which a small number of voters disagree by a very large margin.
